Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-05-28 tests-orbit.tex
Minor revision to orszag-tang section.

\begin{figure}
\begin{center}
\includegraphics[width=0.45\textwidth]{figures/TestOrbit_xy.eps}
\includegraphics[width=0.45\textwidth]{figures/TestOrbit_TotalEnergy.eps}
\caption{Test particle behavior in the Orbit problem, which is used to
test the gravity solver and particle integration.  An effectively
massless test particle is set in circular orbit around a massive
central particle, with the gravitational potential calculated on a 3D,
$32^3$ grid, and evolved forward in time for 200 orbits.  Left panel:
path of the test particle in the orbital plane plotted for the
duration of the simulation.  Right panel: total specific energy
(kinetic plus potential) for the test particle for the duration of the
simulation.  The particle's mean energy (integrated over the length of
the simulation) is represented by a horizontal dashed line, and +/-
one standard deviation by horizontal dotted lines.  All quantities are
in dimensionless units.}
\label{fig.orbittest}
\end{center}
\end{figure}

The ``orbit test'' simulates the orbit of an effectively massless
particle around a massive primary particle and is used to test the
accuracy of both the gravity solver and particle integration.  In this
problem (shown in Figure~\ref{fig.orbittest}), a 3D box with unit size
and $32^3$ grid is created, and a particle with mass 1 is placed at
the center of the box (both box length and particle mass are in
dimensionless units).  A second ``test'' particle, with mass of $10^{-6}$,
is placed at a distance of 0.3 L$_{box}$ from the primary particle in
the x-y plane (at $z=0.5$~L$_{box}$).  Both particles are given
velocities such that they will orbit their common center of mass in
the x-y plane.  The simulation is run for 200 orbits, writing
out a dataset 
approximately once per orbit (with the particle positions being
written out several hundred times per orbit).

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.45\textwidth]{figures/TestOrbit_xy.eps}
\includegraphics[width=0.45\textwidth]{figures/TestOrbit_TotalEnergy.eps}
\caption{Test particle behavior in the Orbit problem, which is used to
test the gravity solver and particle integration.  An effectively
massless test particle is set in circular orbit around a massive
central particle, with the gravitational potential calculated on a 3D,
$32^3$ grid, and evolved forward in time for 200 orbits.  Left panel:
path of the test particle in the orbital plane plotted for the
duration of the simulation.  Right panel: total specific energy
(kinetic plus potential) for the test particle for the duration of the
simulation.  The particle's mean energy (integrated over the length of
the simulation) is represented by a horizontal dashed line, and +/-
one standard deviation by horizontal dotted lines.  All quantities are
in arbitrary units.}
\label{fig.orbittest}
\end{center}
\end{figure}

The ``orbit test'' simulates the orbit of an effectively massless
particle around a massive primary particle and is used to test the
accuracy of both the gravity solver and particle integration.  In this
problem (shown in Figure~\ref{fig.orbittest}), a 3D box with unit size
and $32^3$ grid is created, and a particle with mass 1 is placed at
the center of the box (both box length and particle mass are in
arbitrary units).  A second ``test'' particle, with mass of $10^{-6}$,
is placed at a distance of 0.3 L$_{box}$ from the primary particle in
the x-y plane (at $z=0.5$~L$_{box}$).  Both particles are given
velocities such that they will orbit their common center of mass in
the x-y plane.  The simulation is run for 200 orbits, writing
out a dataset 
approximately once per orbit (with the particle positions being
written out several hundred times per orbit).
